formula1_allyears

### 2020-08-27 inst/formula1_allyears.Rmd
formula 1 all years just the top competitors

@@

>>>>

*Takes about 20 minutes to run with no cache*

@@

```{r}
howmanyraces <- sort(rowSums(M,na.rm=TRUE),decreasing=TRUE)
plot(howmanyraces)
```

```{r}
select <- function(F1tab,minraces=5){
	wanted <- rownames(M)[howmanyraces >= minraces]
	ordertable2supp(F1tab[rownames(F1tab) %in% wanted,])
}
```

```{r,definefreqrace}
freqracers <- function(minraces){
(
	select(f(read.table("formula1_2010.txt")),minraces) + 
	select(f(read.table("formula1_2011.txt")),minraces) + 
	select(f(read.table("formula1_2012.txt")),minraces) + 
	select(f(read.table("formula1_2013.txt")),minraces) + 
	select(f(read.table("formula1_2014.txt")),minraces) + 
	select(f(read.table("formula1_2015.txt")),minraces) + 
	select(f(read.table("formula1_2016.txt")),minraces) + 
	select(f(read.table("formula1_2017.txt")),minraces) + 
	select(f(read.table("formula1_2018.txt")),minraces) 
	)
}

comp <- function(m,mr){
	par(pty="s")
#	plot(m,mr,asp=1,xlim=c(0,0.2),ylim=c(0,0.2))
	plot(m,mr,asp=1)
	abline(0,1)
}
```

# All drivers

```{r,freqtop1,cache=TRUE}
F1_top1 <- freqracers(1)
m1 <- maxp(F1_top1)
pnames(F1_top1) <- rev(pnames(F1_top1))
m1r <- rev(maxp(F1_top1)) # reverse of MLE with names reversed
```

```{r}
pie(m1)
comp(m1,m1r)
```

# Drivers with >= 2 races

```{r,freqtop2,cache=TRUE}
F1_top2 <- freqracers(2)
m2 <- maxp(F1_top2)
pnames(F1_top2) <- rev(pnames(F1_top2))
m2r <- rev(maxp(F1_top2)) # reverse of MLE with names reversed
```

```{r}
pie(m2)
comp(m2,m2r)
```

# Drivers with >= 3 races

```{r,freqtop3,cache=TRUE}
F1_top3 <- freqracers(3)
m3 <- maxp(F1_top3)
pnames(F1_top3) <- rev(pnames(F1_top3))
m3r <- rev(maxp(F1_top3)) # reverse of MLE with names reversed
```

```{r}
pie(m3)
comp(m3,m3r)
```

# Drivers with >= 4 races

```{r,freqtop4,cache=TRUE}
F1_top4 <- freqracers(4)
m4 <- maxp(F1_top4)
pnames(F1_top4) <- rev(pnames(F1_top4))
m4r <- rev(maxp(F1_top4)) # reverse of MLE with names reversed
```

```{r}
pie(m4)
comp(m4,m4r)
```

# Drivers with >= 5 races

```{r,freqtop5,cache=TRUE}
F1_top5 <- freqracers(5)
m5 <- maxp(F1_top5)
pnames(F1_top5) <- rev(pnames(F1_top5))
m5r <- rev(maxp(F1_top5)) # reverse of MLE with names reversed
```

```{r}
pie(m5)
comp(m5,m5r)
```

# Drivers with >= 6 races

```{r,freqtop6,cache=TRUE}
F1_top6 <- freqracers(6)
m6 <- maxp(F1_top6)
pnames(F1_top6) <- rev(pnames(F1_top6))
m6r <- rev(maxp(F1_top6)) # reverse of MLE with names reversed
```

```{r}
pie(m6)
comp(m6,m6r)
```
